%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{xcolor}
\begin{document}
	
	

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Runbo(Chuck)}{Zhao}{ % Your name
\urlstyle{same}\url{https://rzhao03.mysite.syr.edu} \\ % Your website, LinkedIn profile or other web address
\href{mailto:runbozhao@hotmail.com}{runbozhao@hotmail.com} | 315.883.9767 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{\href{https://www.syracuse.edu/}{Syracuse University, USA}}

\descript{MSc., Computer And Information Science}
\location{Grad. Dec 2018 | Syracuse, NY \\ GPA: 3.9/4.0}

\sectionspace % Some whitespace after the section


%------------------------------------------------

\subsection{\href{http://en.xidian.edu.cn/}{Xidian University, China}}
\descript{BEng., Mathematics And Applied Mathematics}
\location{Grad. June 2016 | Xi'an, China}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/runbo94}{\bf Runbo94} \\
LinkedIn:// \href{https://www.linkedin.com/in/runbo94}{\bf Runbo94} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

Internet Programming\\
Object Oriented Programming C++\\
Software Engineering\\
Operating System\\
Mathematics Basis for Computing\\
Design and Analysis of Algorithm\\
Computer Architecture\\
Introduction to Database Management System\\
Randomized Algorithms: Think and Code\\
Structured Programming and Formal method\\


%------------------------------------------------

% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
Java \textbullet{} JavaScript \textbullet{} TypeScript\textbullet{}Matlab \\ 
\location{Over 1000 lines:}
CSS \textbullet{} HTML \textbullet{} SQL \textbullet{} \LaTeX \textbullet{} C++
\\C  \textbullet{} Haskell\\
\location{Familiar:}
NoSQL 
\subsection{Framework}
Angular \textbullet{} React \textbullet{} Express.js \\ Hapi.js
\subsection{Database}
MongoDB \\ Firebase Real-time databse
\subsection{Other tools}
Git \textbullet{} npm \textbullet{} Heroku \textbullet{} PostMan

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}

\runsubsection{Syracuse University(E\&CS)}
\descript{| UI developer (Unpaid intern)}
\location{February 2019 - Now}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\vspace{\topsep}
\begin{tightitemize}
	\item Built the responsive Navbar \& Modals with Bulma by using HTML5, CSS3 \& JSX.
	\item Designed the core components with CRUD operations and RESTful routing with the use of react-router-dom.
	\item Developed the Container components to subscribe to the Redux state.
	\item Connected React with Redux by using the Provider of react-redux and created the single store.
	\item Created actions with Action Creator and applied redux-thunk middleware to the store to handle Async actions.
	\item Developed Reducer functions to handle the state data changes and used axios to make HTTP request to persist the data in the database.
	\item Implemented RWD such as page layouts, menu, navigation buttons, icons and drop-down lists.
	\item Implemented the server-side with Node.js, Express.js and connected it with MongoDB by using mongoose.
	\item Used connect, mapStateToProps and mapDispatchToProps to connect the application with the store.
	\item Created database Schema with mongoose based on the data flow requirements and features.
	\item Performed Unit testing for some modules and features with Jest in the development process.
	\item Implemented RESTful Services with HTTP methods like GET, POST, PUT \& DELETE.
	\item Worked on the document-oriented NoSQL database program - MongoDB for consistent data storing by using JSON-like documents with Database schema.
	
\end{tightitemize}
\sectionspace
%------------------------------------------------
% Project
%------------------------------------------------
\section{Project}

\runsubsection{\href{www.gitgroup2018.com}{www.gitgroup2018.com}}
\descript{| A web based software development management system}
\location{September 2018 – Now}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
	\item Seamless integration with GitHub keeps all of your GitHub Issue data in sync across both platforms in real time.
	\item Access the GitHub personal data via GitHub REST API v3. Authorize users through GitHub OAuth APP three steps.
	\item Drag and drop the card among different columns which represent different stage of the development process. Implement beautiful, natural movement of draggable and droppable items. Draw a variety of Agile charts using ReCharts.
	\item Use highly-productive Typescript to build Node server.
	\item \textbf{Tools}: HTML5, CSS3, Bulma, React, TypeScript, ts-node, MLab, Heroku
\end{tightitemize}





\sectionspace % Some whitespace after the section

\runsubsection{Nachos Operating System}
\descript{| Not Another Completely Heuristic Operating System}
\location{August 2018 – December 2018}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

%------------------------------------------------


%------------------------------------------------
%\runsubsection{Health Center Database Design}
%\descript{| An Online movie rating and renting service}
%\location{October 2016 – February 2017}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightitemize}
%\item Store the data for Patient, Visitor, Billing, Insurance, Employees, Patient Room, Patient Health Histories. Design a Descriptive ERD.
%\item Implement the DB by MicroSoft SQL Server. Create the tables, columns, primary keys, datatypes, nullabilities, and relationships. Implement views and stored procedures.
%\item \textbf{Tools}: Microsoft SQL Server, Microsoft Visio
%\end{tightitemize}


%------------------------------------------------
% Research
%------------------------------------------------

%\section{Research}

%\runsubsection{PageRank Based Analysis of Network Node Influence}
%\descript{}

%\location{July 2014 – September 2014}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightitemize}
%	\item Treat edge weight as a new input and got improved PageRank algorithm, extended the original PageRank iteration formula from one dimension to multi dimension.
%	\item Take Erdos scholar network and Chinese social networks as examples and verified the reliability of the algorithm.
%\end{tightitemize}

%\sectionspace % Some whitespace after the section

%------------------------------------------------

%\runsubsection{Cornell Phonetics Lab}
%\descript{| Head Undergraduate Researcher}
%
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
%
%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

%\section{Awards} 
%
%\begin{tabular}{rll}
%2014	 & top 52/2500 & KPCB Engineering Fellow\\
%2014	 & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
%2014	 & 1\textsuperscript{st}/50 & Microsoft Coding Competition, Cornell\\
%2013	 & National & Jump Trading Challenge Finalist\\
%2013 & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament \\
%2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010 & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Societies} 
%
%\begin{tabular}{rll}
%2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
%2014 & National & The Global Leadership and Education Forum (tGELF)\\
%2012 & National & Golden Key International Honor Society\\
%2012 & National & National Society of Collegiate Scholars\\
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------
\newpage % Start a new page

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

\end{minipage} % The end of the left column
%\hfill
\begin{minipage}[t]{1\textwidth} % The right column takes up 66% of the text width of the page
\begin{tightitemize}
	\item Added multi-threading capabilities to Nachos.
	\item Created Process functions and Thread Fork functions like FORK, TERMINATE \& JOIN.
	\item Implemented several system call routines for user programs and round-robin scheduling like FORK\_POS, WAIT\_POS, EXIT\_POS.
	\item Implemented Round-robin scheduling. Round-robin scheduling gives each process a fix time slice to run.
	\item \textbf{Tools}: C++, Vscode, Linux
\end{tightitemize}

\sectionspace % Some whitespace after the section
\runsubsection{\href{www.jajang.cloud}{www.jajang.cloud}}
\descript{| A cloud-based restaurant management plateform service, designed for the small and medium restaurants.}
\location{October 2017 – April 2018}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
	\item Implement the table status monitor function by the Firebase realtime database. The RxJs makes it possible to do real-time, bidirectional and event-based communication between managers and customers.
	\item Achieve basic E-commence functions, such as: authentication and authorization, product lists, shopping cart, etc.(see\href{https://github.com/Runbo94/JaJang-report}{Runbo94/JaJang-report}). Also, to make JaJang more functional,some third-part modules is imported in JaJang such as: \href{https://github.com/laixiangran/e-ngx-print}{e-ngx-print}, \href{https://github.com/nacardin/ngx-qrcode}{ngx-qrcode},
	\href{https://www.npmjs.com/package/neu-charts}{neu-charts}.
	\item  Beautiful style of pages including some animation and fashion web component like card, carousel, modal. Also ng-bootstrap is also well designed for responsive pages, which is suitable for using JaJang on both PC and mobile platform.
	\item \textbf{Tools}: HTML5, CSS3, Bootstrap, TypeScript, Angular5, Firebase
\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{\href{www.renmovie123.com}{www.renmovie123.com}}
\descript{| An Online movie rating and renting service}
\location{May 2018 – September 2018}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
	\item Full-stack developed using React + Express + MongoDB model.
	deployed by Heroku.
	\item Build the frontend by React with some key components, including functional and well OOP Designed List component, implementing pagination, filtering, and sorting, Form component implementing submission and validation. etc.
	\item Using Node.js to design the restful API backend and do fully unit test and integration test by Jest.
	\item \textbf{Tools}: HTML5, CSS3, Bootstrap, JavaScript, React, NodeJs, ExpressJs, MongoDB
\end{tightitemize}
%\section{Example Section 2}
\section{Research}

\runsubsection{PageRank Based Analysis of Network Node Influence}
\descript{}

\location{July 2014 – September 2014}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
	\item Treat edge weight as a new input and got improved PageRank algorithm, extended the original PageRank iteration formula from one dimension to multi dimension.
	\item Take Erdos scholar network and Chinese social networks as examples and verified the reliability of the algorithm.
\end{tightitemize}

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}